\begin{thebibliography}{9999}
\addcontentsline{toc}{chapter}{Bibliography}

\bibitem{baladi}
V.~Baladi,  \newblock {\em Positive Transfer Operators and Decay of Correlations}.
\newblock Advanced Series in Nonlinear Dynamics, 2000.

\bibitem{chekroun}
M.~D.~Chekroun, J.~D.~Neelin, D.~Kondrashov, J.~C.~McWilliams, M.~Ghil, Rough Parameter Dependence and the Role of Ruelle-Pollicot Resonances, \emph{PNAS}, Vol: 111(5), 1684--1690, 2014.

\bibitem{dobrushin}
R.~L.~Dobrushin, Theory of Probability and its Applications, \emph{Theory of Probability and its Applications}, Vol: 1(1), 65--80, 1956

\bibitem{gaio}
M.~Dellnitz, G.~Froylan, O.~Junge, \emph{The Algorithmns Behind GAIO--Set Oriented Numerical Methods for Dynamical Systems} in: \emph{Ergodic Theory, Analysis} and Efficient Simulation of Dynamical Systems, Springer, 2001.

\bibitem{kubo}
R.~Kubo, Statistical-mechanical Theory of Irreversible Processes. I. General Theory and simple Applications to Magnetic and Conduction Problems, \emph{J. Phys. Soc. Jpn.}, Vol: 12, 570--586, 1957.

\bibitem{hairer}
M.~Hairer,A.~J.~Majda, A Simple Framework to Justify Response Theory, \emph{Nonlinearity}, Vol: 23, 909--922, 2010.

\bibitem{henon} M. H\'{e}non, A Two Dimensional Map with a Strange Attractor.
\newblock {\em Comm. Math. Phys.}, 50:69--77, 1976.

\bibitem{liverani}
G.~Keller,C.~Liverani, Stability of the Spectrum for Transfer Operators, \emph{Annali della Scuola Normale Superiore di Pisa}, Vol: 28(1), 141--152, 1999.

\bibitem{lasota}
A.~Lasota, M.~C.~Mackey, \emph{Chaos, Fractals, and Noise Stochastic Aspects of Dynamics}, Springer-Verlag, 1991.

\bibitem{lacorata}
G.~Lacorata, A.~Vulpiani, Fluctuation-Response Relation and Modelling in Systems with Fast and Slow Dynamics, \emph{Nonlinear Processes in Geophysics}, Vol: 14, 681--694, 2007.

\bibitem{liverani}
G.~Keller, C.~Liverani, Stability of the Spectrum for Transfer Operators, \emph{Annali della Scuola Normale Superiore di Pisa}, Vol: 28, 141--152, 1999.

\bibitem{lorenz63}
E.~N.~Lorenz, Deterministic Nonperiodic Flow, \emph{Journal of the Atmospheric Sciences}, Vol: 20, 130--141, 1963.

\bibitem{lorenz84}
E.~N.~Lorenz, Deterministic Nonperiodic Flow, \emph{Tellus}, Vol: 36A, 98--110, 1984.

\bibitem{lucarini}
V.~Lucarini, Response Operators for Markov Processes in a Finite State Space: Radius of Convergence and Link to the Response Theory for Axiom A Systems, \emph{Journal of Statistical Mechanics}, Vol: 162, 312--333, 2016.

\bibitem{leith}
C.~E.~Leith, Climate Response and Fluctuation Dissipation, \emph{Journal of the Atmospheric Sciences}, Vol: 32, 2022--2026, 1975.

\bibitem{pazy}
A.~Pazy, \emph{Semigroups of Linear Operators and Applications to Partial Differential Equations}. Applied Mathematical Sciences, Springer-Verlag New York, 1983.

\bibitem{review}
U.~M.~B.~Marconi, A.~Puglisi, L.~Rondoni, A.~Vulpiani, Fluctiation-Dissipation: Response Theory in Statistical Physics, \emph{Physics Reports}, Vol: 461, 111--195, 2008.

\bibitem{ruelle}
D.~Ruelle, A Review of Linear Response Theory for General Differentiable Dynamical Systems, \emph{Nonlinearity}, Vol: 22, 855--870, 2009.

\bibitem{ruellee}
D.~Ruelle, \emph{Thermodynamic Formalism}. Cambridge Mathematical Library, 2004.

\bibitem{tantet}
A.~Tantet,V.~Lucarini, H.~A.~Dijkstra, Resonances in a Chaotic Attractor Crisis of the Lorenz Flow, \emph{Journal of Statistical Physics}, Vol: 170, 584--616, 2018.

\bibitem{trefethenps}
N.~L.~Trefethen, M.~Embree, \newblock {\em Spectra and Pseudospectra}.
\newblock Princeton University Press, 2005.

\bibitem{vulpiani}
G.~Boffeta, G.~Lacorata, S.~Musacchio, A.~Vulpiani, Relaxation of Finite Perturbations: Beyond the Fluctuation Response Relation, \emph{Chaos}, Vol: 13(3), 806--811, 2003.

\end{thebibliography} 